Individual Differenes

### 2023-08-18 Analysis/e1_Analysis.qmd
Inspect Bayesian marginal effects in E1 Test
e2 and e3 bayesian fits

---
title: Experiment 1 Analysis
date: last-modified
categories: [Analysis, R]
page-layout: full
# fig-width: 15
# fig-height: 8
toc: false
---

@@

>>>>

---
title: E1 Extras
date: last-modified
categories: [Analysis, R]
page-layout: full
# fig-width: 15
# fig-height: 8
toc: false
---

@@

#test %>% group_by(id,vb,condit) |> plot_distByCondit()

### 2023-08-18 Misc/indv_diff.qmd
e2 and e3 bayesian fits

@@

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1000) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

>>>>

indv_coefs |> ggplot(aes(y=id, x=Estimate.bandInt)) + geom_pointrange()

random_effects <- e1_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 2000) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(test$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

cd <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  mutate(Slope=bandInt_RF+b_bandInt) |> group_by(id)

cdMed <- cd |> group_by(id) |> median_qi(Slope) |> mutate(rankSlope=rank(Slope)) |> arrange(rankSlope) |> left_join(e1Sbjs, by=join_by(id))

cdMed %>% ggplot(aes(y=rankSlope, x=Slope,fill=condit,color=condit)) + 
  geom_pointrange(aes(xmin=.lower , xmax=.upper)) + 
  labs(x="Estimated Slope", y="Participant") # + facet_wrap(~condit) +

cd |>  ggplot(aes(y=id, x=Slope)) + geom_pointrange()
```

@@
